Capital Budget Funding in Toronto

### 2024-09-26 paper/paper.qmd
added all 4 scatterplots and a bar graph to quarto

@@

```{r Figure 1, echo=FALSE, message=FALSE, warning=FALSE}
#| label: fid-householdincome

@@

FIGURE 1 HERE (MAYBE BOTH WITH WARD 13 AND WITHOUT WARD 13)

@@

INSERT FIGURE 2 HERE
```{r Figure 2, echo=FALSE, message=FALSE, warning=FALSE}
#| label: fid-lowincome

@@

ggplot(filtered_data, aes(x = as.numeric(`Prevalence of low income based on the Low-income measure, after tax (LIM-AT) (%)`), y = per_capita_funding)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(
    title = "Per Capita Funding vs Prevalence of low income",
    x = "Prevalence of low income (%)",
    y = "Per Capita Funding ($)"
  ) +
  scale_x_continuous(labels = percent_format()) +
  scale_y_continuous(labels = dollar_format()) +
  theme_minimal()
```
```

@@

FIGURE 3 HERE !!!

@@

FIGURE 4 HERE!!!

>>>>

```{r Figure 1, echo=FALSE, message=FALSE, warning=FALSE}
#| label: fig-percapitafunding
# Wards by Per Capita Funding
ggplot(merged_data, aes(x = reorder(`Ward Number`, per_capita_funding), y = per_capita_funding)) +
  geom_bar(stat = "identity", fill = "#0072B2") +
  labs(
    title = "Wards by Per Capita Funding",
    x = "Ward Number",
    y = "Per Capita Funding ($CAD)"
  ) +
  scale_y_continuous(labels = dollar_format()) +
  theme_minimal(base_family = "Helvetica") +
  theme(
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
    axis.text.x = element_text(angle = 45, hjust = 1, size = 12),
    axis.title = element_text(size = 14)
  )
```

@@

```{r Figure 2, echo=FALSE, message=FALSE, warning=FALSE}
#| label: fig-householdincome

@@

@@

```{r Figure 3, echo=FALSE, message=FALSE, warning=FALSE}
#| label: fig-lowincome

# Scatter plot of Per Capita Funding vs Prevalence of low income with ward 13 removed

@@

ggplot(filtered_data, aes(x = as.numeric(`Prevalence of low income based on the Low-income measure, after tax (LIM-AT) (%)`), y = per_capita_funding)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(
    title = "Per Capita Funding vs Prevalence of low income",
    x = "Prevalence of low income (%)",
    y = "Per Capita Funding ($)"
  ) +
  scale_x_continuous(labels = percent_format()) +
  scale_y_continuous(labels = dollar_format()) +
  theme_minimal()
```

@@

```{r Figure 4, echo=FALSE, message=FALSE, warning=FALSE}
#| label: fig-education

# Scatter plot of Per Capita Funding vs Bachelor's Degree of Higher with ward 13 removed

ggplot(filtered_data, aes(x = as.numeric(`Bachelor’s degree or higher per capita`), y = per_capita_funding)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(
    title = "Per Capita Funding vs Bachelor's degree or higher",
    x = "Attained Bachelor's degree or higher (%)",
    y = "Per Capita Funding ($)"
  ) +
  scale_x_continuous(labels = percent_format()) +
  scale_y_continuous(labels = dollar_format()) +
  theme_minimal()
```

@@

```{r Figure 5, echo=FALSE, message=FALSE, warning=FALSE}
#| label: fig-minority

# Scatter plot of Per Capita Funding vs Minority Population with ward 13 removed

ggplot(filtered_data, aes(x = as.numeric(`Total visible minority population per capita`), y = per_capita_funding)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(
    title = "Per Capita Funding vs Visible Minority Population",
    x = "Visible Minority Population (%)",
    y = "Per Capita Funding ($)"
  ) +
  scale_x_continuous(labels = percent_format()) +
  scale_y_continuous(labels = dollar_format()) +
  theme_minimal()
```
